Cryptographic assurance of secrecy and fairness in voting

### 2012-12-05 paper/paper.tex
Move coercion section next to secrecy
restructure Background into Verifiability and Secrecy sections

% don't number sections
\setcounter{secnumdepth}{0}

@@

\section{Background}

An election involves an information exchange between many independent \term{voters} and a single
\term{election authority} organization.
In a verifiable election, each voter may verify that her own vote was counted correctly
by the election authority.
A voter, or any other third party \term{auditor}, may also verify the accuracy of the final tallies
reported by the election authority. \cite{preta}

@@

>>>>

% don't number sections
%\setcounter{secnumdepth}{0}

@@

An election involves an information exchange between many independent \term{voters} and a single
\term{election authority} organization.
In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
by the election authority.
A voter, or any other third party \term{auditor}, may also verify the accuracy of the final tallies
reported by the election authority. \cite{preta}
Voting is complicated by the requirement that all votes be secretive to avoid coercion.

\section{Verifiability}

@@

\section{Ballot secrecy}

It is often necessary to maintain secrecy of invididuals' votes, to avoid the possibility
that a voter may receive either retribution or reward.
We give two definitions of ballot secrecy: \term{privacy} and \term{receipt-freeness}.

\subsection{Privacy}

\subsection{Receipt-freeness}

\subsection{Stuff that will be moved into one of the previous sections}
